Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-12 providence/sections/workload.tex
more

Recall from Section~\ref{sec:pilot} that the pilot \Providence RLA performed in Providence, Rhode Island had an SO \BRAVO \emph{misleading sequence}. In particular, the audit passed with an SO \BRAVO risk measure of $5.41\%$ but the final cumulative tally of the sample gives a \BRAVO risk measure of $36.6\%$.

>>>>

Recall from Section~\ref{sec:pilot} that the pilot \Providence RLA performed in Providence, Rhode Island had an SO \BRAVO \emph{misleading sequence}. In particular, the audit passed with an SO \BRAVO risk measure of $0.0541$ but the final cumulative tally of the sample gives a \BRAVO risk measure of $0.366$.
